%\requirepackage{lineno}
\documentclass[11pt]{article}
\usepackage[left=4cm,top=3cm,right=3cm,left=3cm,nofoot]{geometry}  \geometry{a4paper}                   
\usepackage{tipa, apalike, graphicx, amssymb, delarray, epstopdf, amsmath, amsthm, setspace, supertabular, qtree, hyperref, footnote, palatino, url, multicol, hanging, fullpage, supertabular, ulem} 
%, lineno, gb4e} % gb4e messes up math mode. 
\clubpenalty=300 \widowpenalty=300
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
%\usepackage[parfill]{parskip} 			%Activate for line, not indent, paragraphs.
\newenvironment{itemise}{
\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{itemize}}

\title{Homework 6}
\author{Richard Littauer \& Lamar Payson}
\date{\today}                          		% Activate to display a given date or no date
\singlespace
\begin{document}
\maketitle
\begin{itemise}
\item A simple one variable linear regression model. We would include our one independent variable, as it's all we've got. See {\it hw6\_addendum} for results. When you look at the anova value, it is clear here that the p value is highly significant. For the summary data, we can see a base intercept of 159wpm, which changes by around 20wpm per drink. The variables are clearly correlated here. 
\item We used the dataset {\it weightRatings} from {\it languageR}. We used the IVs Sex and Class on the DV rating. 

For the main effects model, we can see that sex is marginally significant, while class is highly significant as a modulator of rating. In the summary, we can see that `male' sex cases a decrease of .16, wile class `plant' causes a decrease of 1.89.

For the interactions model, we see that the p value is statistically insignificant at .70. 

See the addendum for the details. 
\end{itemise}






















%\bibliographystyle{apasoft}
%\bibliography{/Users/richardlittauer/Desktop..}
\end{document}