%\requirepackage{lineno}
\documentclass[11pt]{amsart}
\usepackage[left=4cm,top=3cm,right=3cm,left=3cm,nofoot]{geometry} 
\geometry{a4paper}                   
\usepackage{tipa, apalike, graphicx, amssymb, delarray, epstopdf, amsmath, amsthm, setspace, supertabular, qtree, hyperref, footnote, palatino, url, multicol, hanging, fullpage}
%\usepackage{lineno}
\clubpenalty=300
\widowpenalty=300
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
%\usepackage[parfill]{parskip} 			%Activate for line, not indent, paragraphs.
%\newcommand{\Env}{\rule{2em}{.5pt}} 	%Defines the phonological environment line
%\renewcommand\ng{\textipa{N}} 		%Defines \ng for the velar nasal
\doublespacing

%Linguistic examples should be italicised when given in standard spelling. Glosses are put in single inverted commas. Use < > when citing a written (historical) source or when an orthographic form is specifically at issue. Use orthographical/historical, < > morphemic { }, morphophonemic || ||, phonemic [ ], and phonetic / / brackets as appropriate. 

\title{Simulating Language Lecture 4, 5}
\author{Simon Kirby \& Andrew Smith}
\date{January 28$^{th}$, 200}                                           % Activate to display a given date or no date

\begin{document}
\maketitle
\section{Simulatin' Language}

Is mutual benefit realistic?\\ \indent
-Depends on the context: are signals related to fitness, are they worth while for the producer, is there a receiver, etc.

Note: Use of various spatiality - using a different signal with nonresponsive agents, and another different one for noticed uninteligble agents? Might be interesting.

\section{Simulatin' Language 5: 4 Feb}
 
 As a model of signalling, what's different: meanin's aren't inherently encoded, language is productive
 
 Connectionism: the idea of an artificial neural network. Based on how the brain works. 
 
 Neural systems are the same as what we've been doing (subtle difference, but I didn't catch it.)
 
 Kirby: One view: learning occurs when an organism changes its internal state on the basis of experience"
 
 Probably wrong. too broad. Data is stored, may involve improvement, doesn't necessarily occur due to experience. 
 
 New learning: innateness gone. Is innateness really gone? Not the vervet monkey system. (As the matrix of zeros is there: should that be innate?)

\end{document}